---
title: "DSC310 Week 2"
author: "Joshua Merrell"
output: 
  md_document:
    variant: markdown_github
---

```{r, libraries}
library(ggplot2)
```

# Week 3
## Histogram
ggplot(diamonds, aes(x=carat, fill = cut)) +
  geom_histogram(binwidth = .17) +
  scale_fill_brewer(palette = 2) +
  theme_classic() +
  ggtitle(label = "Diamonds Histogram", 
          subtitle = "Joshua Merrell\nDSC310 Week 3")

## Density Plot
ggplot(diamonds, aes(x = carat, fill = cut)) +
  geom_density() +
  theme_classic() +
  scale_fill_brewer(palette = 2) +
  ggtitle(label = "Diamonds Density Plot", 
          subtitle = "Joshua Merrell\nDSC310 Week 3")

## Boxplot
ggplot(diamonds, aes(x = carat, fill = cut)) +
  geom_boxplot() +
  coord_flip() +
  scale_fill_brewer(palette = 2) +
  theme_classic() +
  ggtitle(label = "Diamonds Boxplot", 
          subtitle = "Joshua Merrell\nDSC310 Week 3")

## Violin Plot
ggplot(diamonds, aes(x = carat, y = carat)) +
  geom_violin(fill = "lightskyblue") +
  scale_fill_brewer(palette = 2) +
  coord_flip() +
  ggtitle(label = "Diamonds Violent Plot",
          subtitle = "Joshua Merrell\nDSC310 Week 3")

# Week 2

## Vertical or Horizontal Barplot
```{r, vertical (stacked) barplot}
qplot(x=cut, fill=color, data=diamonds) + 
    theme(plot.background = element_rect(fill="gray")) + 
    ggtitle("Joshua Merrell\nDSC310 Wk2 Pt 1-a: R Barplot\nggplot2::diamonds")
```

## Grouped or stacked bar chart
```{r grouped barplot}
ggplot(data=diamonds, aes(fill=clarity, x=cut)) +
  geom_bar(position="dodge") +
  theme(plot.background = element_rect("gray")) +
  ggtitle("Joshua Merrell\nDSC310 Wk2 Pt 2-a: R Grouped Barplot\nggplot2::diamonds")
```

## Heatmap:
```{r heatmap}
ggplot(as.data.frame(table(diamonds[ ,c("cut", "clarity")])), 
       aes(x = cut, y = clarity)) + 
  geom_tile(aes(fill = Freq)) +
  geom_text(aes(label = Freq), col = 'yellow') + 
  theme(plot.background = element_rect("gray")) +
  ggtitle("Joshua Merrell\nDSC310 Wk2 Pt 3-a: R Heatmap\nggplot2::diamonds")
```
